Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2020-11-18 ms/main.tex
morrison

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \pagebreak
% Acknowledgements
{\small
\section*{Acknowledgements}
We thank Lilach Hadany, Ayelet Shavit, and Kaleda Krebs Denton for discussions and comments.
This work was supported in part by
the Israel Science Foundation 552/19 (YR),
and Minerva Stiftung Center for Lab Evolution (YR).
% TODO funding for other authors?
}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \pagebreak
% Acknowledgements
{\small
\section*{Acknowledgements}
We thank Lilach Hadany, Ayelet Shavit, and Kaleda Krebs Denton for discussions and comments.
This work was supported in part by
the Israel Science Foundation 552/19 (YR),
Minerva Stiftung Center for Lab Evolution (YR),
and the Morrison Institute for Population and Resources Studies at Stanford University (MWF).
